---
title: "Binary-Classifier-Data"
author: "Rahimian Yousof"
date: "11/6/2021"
output:
  word_document: default
  html_document: default
  pdf_document: default
---
**Fit a logistic regression model to the binary-classifier-data.csv dataset**


## Set the working directory to the root of your DSC 520 directory
```{r}
setwd("C:/Users/Yousof/Desktop/DSC 520/week 10")
```

## load the 'binary-classifier-data.csv' to 
```{r}
binary_classifier_data <- read.csv("C:/Users/Yousof/Desktop/DSC 520/week 10/binary-classifier-data.csv")
```

## Fit a logistic regression model to the binary-classifier-data.csv data set
```{r}
binary_classifier_data_glm <- glm(label ~ ., 
                                  data=binary_classifier_data, family = binomial(link = "logit"))
binary_classifier_data_glm
```
## Create a coefficent plot 
```{r}
library(coefplot)
coefplot(binary_classifier_data_glm)
```

## Get the summary of 'binary_classifier-data_glm'
```{r}
summary(binary_classifier_data_glm)
```

## Create a plot for binary_classifier_data_glm
```{r}
plot(binary_classifier_data_glm)
```
